### 2019-07-22 1_introduction.tex
Run spell check.

We present Task Bench, a benchmark designed for exploring the performance
behaviors of parallel and distributed programming systems under a
variety of conditions.  The key property of TaskBench is that it completely separates
the implementation of TaskBench for a new system to be measured from the implementation
of a new benchmark application to be run on the systems supported by TaskBench.
In all benchmarks we know of, the effort to implement $n$ benchmarks on $m$
systems is $\mathcal{O}(mn)$.  TaskBench's design reduce the work to $\mathcal{O}(m) + \mathcal{O}(n)$,
enbaling dramatically more systems and benchmarks to be explored for the same amount of programming
effort.  New benchmarks created with Task Bench
immediately run on all systems, and new systems immediately run all
benchmarks.

@@

Adding a new programming system to Task Bench involves  implementing a set of standard
services, such as executing a task or a data transfer.  This interface is simple enough to 
be implemented with reasonable effort to a level of quality sufficient for comparative
studies. Task Bench also provides a core library that encapsulates the functionality
shared by all system implementations, which not only reduces the implementation effot
required but also makes it much easier to achieve truly apples-to-apples comparisons
between systems.

@@

To characterize the contribution of a programming model's runtime
system to application performance, and as an example of the novel studies that can be done
with Task Bench, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively, for a given
workload, METG(50\%) is the smallest task granularity that maintains
at least 50\% efficiency, meaning that the application achieves at
least 50\% of peak performance (e.g., FLOP/s or memory bandwidth) on a
given machine. METG captures the essence of what is important in a
weak or strong scaling study, the behavior at the limit of
scalability. For weak scaling, METG(50\%) corresponds directly to the
smallest problem size that can be weak-scaled with 50\%
efficiency. For strong scaling, METG(50\%) can be used to compute the
scale at which performance can be expected to dip below 50\%
efficiency.  We note that METG(50\%) for a given runtime system will
vary with the particular application and the underlying hardware---i.e., METG(50%)
is not a constant for a given system, but we will see that individual systems have
a characteristic ranges of METG(50\%) values and that there is additional insight
in the reasons that the mininum effective task granularity can vary.

>>>>

We present Task Bench, a benchmark designed for exploring the performance
behaviors of parallel and distributed programming systems under a
variety of conditions.  The key property of Task Bench is that it completely separates
the implementation of Task Bench for a new system to be measured from the implementation
of a new benchmark application to be run on the systems supported by Task Bench.
In all benchmarks we know of, the effort to implement $n$ benchmarks on $m$
systems is $\mathcal{O}(mn)$.  Task Bench's design reduce the work to $\mathcal{O}(m + n)$,
enabling dramatically more systems and benchmarks to be explored for the same amount of programming
effort.  New benchmarks created with Task Bench
immediately run on all systems, and new systems immediately run all
benchmarks.

@@

Adding a new programming system to Task Bench involves  implementing a set of standard
services, such as executing a task or a data transfer.  This interface is simple enough to 
be implemented with reasonable effort to a level of quality sufficient for comparative
studies. Task Bench also provides a core library that encapsulates the functionality
shared by all system implementations, which not only reduces the implementation effort
required but also makes it much easier to achieve truly apples-to-apples comparisons
between systems.

@@

To characterize the contribution of a programming model's runtime
system to application performance, and as an example of the novel studies that can be done
with Task Bench, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively, for a given
workload, METG(50\%) is the smallest task granularity that maintains
at least 50\% efficiency, meaning that the application achieves at
least 50\% of peak performance (e.g., FLOP/s or memory bandwidth) on a
given machine. METG captures the essence of what is important in a
weak or strong scaling study, the behavior at the limit of
scalability. For weak scaling, METG(50\%) corresponds directly to the
smallest problem size that can be weak-scaled with 50\%
efficiency. For strong scaling, METG(50\%) can be used to compute the
scale at which performance can be expected to dip below 50\%
efficiency.  We note that METG(50\%) for a given runtime system will
vary with the particular application and the underlying hardware---i.e., METG(50%)
is not a constant for a given system, but we will see that individual systems have
a characteristic ranges of METG(50\%) values and that there is additional insight
in the reasons that the minimum effective task granularity can vary.
